---
title: "Child & Youth Mental Health Division Learning Platform"
date: "`r Sys.Date()`"
description: |
    Summarized results of the Spring 2022 survey.
output:
  html_document:
    theme: cosmo
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
    toc_depth: 2
    df_print: paged
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  comment = "##",
  R.options = list(width = 60)
)
```

```{r load_libraries}
library(dplyr)
library(forcats)
library(glue)
library(gt)
library(gtExtras)
library(gtsummary)
library(here)
library(readr)
library(stringr)
library(tidyr)
```

## Overview

```{r}
df <-
  read_csv(here("data", "ChildYouthMentalHeal_DATA_2022-07-04_0939.csv"), na = c("", "NA", "N/A", "none", "?")) %>%
  select(-redcap_survey_identifier) %>%
  filter(!is.na(survey_01)) %>%
  filter(!record_id %in% c(4, 17, 20)) %>%
  mutate(site = recode(survey_01,
                       "1" = "Centre for Addiction and Mental Health",
                       "3" = "Garry Hurvitz Centre for Community Mental Health",
                       "4" = "George Hull Centre for Children and Families",
                       "5" = "Humber River Hospital",
                       "6" = "Michael Garron Hospital",
                       "7" = "North York General Hospital",
                       "8" = "Ontario Shores",
                       "9" = "Scarborough Health Network",
                       "10" = "Hospital for Sick Children",
                       "11" = "Sunnybrook Health Sciences Centre",
                       "12" = "Trillium Health Partners",
                       "13" = "Unity Health",
                       "14" = "University of Toronto Health & Wellness",
                       "15" = "Women's College Hospital",
                       "16" = "Youthdale Treatment Centres"))
```

```{r}
full_site_list <- c("Centre for Addiction and Mental Health",
                    "Garry Hurvitz Centre for Community Mental Health",
                    "George Hull Centre for Children and Families",
                    "Humber River Hospital",
                    "Michael Garron Hospital",
                    "North York General Hospital",
                    "Ontario Shores",
                    "Scarborough Health Network",
                    "Hospital for Sick Children",
                    "Sunnybrook Health Sciences Centre",
                    "Trillium Health Partners",
                    "Unity Health",
                    "University of Toronto Health & Wellness",
                    "Women's College Hospital",
                    "Youthdale Treatment Centres"
)

missing_sites <- setdiff(full_site_list, df$site)
```

```{r}
df <-
  df %>%
  add_row(site = missing_sites, spring_2022_survey_complete = rep(999, length(missing_sites))) %>%
  select(site, everything()) %>%
  arrange(site) %>%
  mutate(site_abbr = case_when(site == "Centre for Addiction and Mental Health" ~ "CAMH",
                               site == "Garry Hurvitz Centre for Community Mental Health" ~ "CCMH",
                               site == "George Hull Centre for Children and Families" ~ "GHC",
                               site == "Humber River Hospital" ~ "HRH",
                               site == "Michael Garron Hospital" ~ "MGH",
                               site == "North York General Hospital" ~ "NYGH",
                               site == "Ontario Shores" ~ "Ontario Shores",
                               site == "Scarborough Health Network" ~ "SHN",
                               site == "Hospital for Sick Children" ~ "SickKids",
                               site == "Sunnybrook Health Sciences Centre" ~ "Sunnybrook",
                               site == "Trillium Health Partners" ~ "THP",
                               site == "Unity Health" ~ "Unity Health",
                               site == "University of Toronto Health & Wellness" ~ "UTHW",
                               site == "Women's College Hospital" ~ "WCH",
                               site == "Youthdale Treatment Centres" ~ "Youthdale")
  )
```

```{r}
sites_completed <-
  df %>%
  mutate(survey_status = recode(spring_2022_survey_complete,
                                "0" = "Responded",
                                "2" = "Responded",
                                "999" = "Did not respond")) %>%
  select(site, site_abbr, survey_status) %>%
  arrange(
    factor(survey_status, levels = c("Responded", "Did not respond"))
  ) %>%
  unique() %>%
  group_by(survey_status) %>%
  gt(rowname_col = "site") %>%
  cols_label(site_abbr = "") %>%
  tab_style(
    style = list(
      cell_text(weight = "bold")
    ),
    locations = cells_row_groups()
  ) %>%
  gt_theme_538()
```

```{r}
df <-
  df %>%
  filter(!is.na(record_id))
```

We received responses from **`r df %>% nrow()`** managers to the survey. Of the responses, **`r df %>% filter(spring_2022_survey_complete == 2) %>% nrow()`** were fully complete and **`r df %>% filter(spring_2022_survey_complete == 0) %>% nrow()`** were partially complete.

The table below summarizes which sites we received responses from:

```{r}
sites_completed
```

```{r}
multi_response <-
  df %>%
  group_by(site_abbr) %>%
  count() %>%
  filter(n > 1)
```

<br>

We received responses from *2* different managers at sites: **`r paste(multi_response$site_abbr, sep=",", collapse=" and ")`**. Where possible, we've only included the unique responses for each site.

## Results

### 3. How do new outpatient clients get into your site/centre?

```{r}
q3 <-
  df %>%
  select(site_abbr, survey_03___1:survey_03_other) %>%
  filter_all(any_vars(. != 0))

q3_uniq_sites <-
  q3 %>%
  select(site_abbr) %>%
  unique() %>%
  nrow()
```

```{r}
q3_results <-
  q3 %>%
  select(-survey_03_other) %>%
  pivot_longer(survey_03___1:survey_03___4, names_to = "referral_source", values_to = "count") %>%
  filter(count == 1) %>%
  unique() %>%
  mutate(referral_source = recode(referral_source,
                                  "survey_03___1" = "Self-referral",
                                  "survey_03___2" = "MD only referral",
                                  "survey_03___3" = "Hospital emergency department or internal referral",
                                  "survey_03___4" = "Other"))

self_ref_sites <-
  q3_results %>%
  filter(referral_source == "Self-referral") %>%
  select(site_abbr) %>%
  unlist %>%
  paste(., collapse=", ")

md_ref_sites <-
  q3_results %>%
  filter(referral_source == "MD only referral") %>%
  select(site_abbr) %>%
  unlist %>%
  paste(., collapse=", ")

hosp_ref_sites <-
  q3_results %>%
  filter(referral_source == "Hospital emergency department or internal referral") %>%
  select(site_abbr) %>%
  unlist %>%
  paste(., collapse=", ")

other_ref_sites <-
  q3_results %>%
  filter(referral_source == "Other") %>%
  select(site_abbr) %>%
  unlist %>%
  paste(., collapse=", ")

q3_results %>%
  group_by(referral_source) %>%
  summarize(count = n()) %>%
  mutate(count_scaled = count/q3_uniq_sites * 100) %>%
  ungroup() %>%
  mutate(site = case_when(referral_source == "Self-referral" ~ self_ref_sites,
                          referral_source == "Hospital emergency department or internal referral" ~ hosp_ref_sites,
                          referral_source == "Other" ~ other_ref_sites,
                          referral_source == "MD only referral" ~ md_ref_sites)) %>%
  arrange(desc(count)) %>%
  gt() %>%
  gt_plt_bar_pct(column = count_scaled, scaled = TRUE) %>%
  cols_label(
    referral_source = "Referral source",
    count = "# of responses",
    count_scaled = "",
    site = "Sites"
  ) %>%
  cols_width(3 ~ px(125)) %>%
  gt_theme_538()
```

<br>

Sites that endorsed other referral sources are summarized below:

```{r}
df %>%
  select(site_abbr, survey_03_other) %>%
  filter(!is.na(survey_03_other)) %>%
  arrange(site_abbr) %>%
  gt() %>%
  cols_label(
    site_abbr = "Site",
    survey_03_other = "Other referral source"
  ) %>%
  gt_theme_538()
```

### 4. Are there exclusion criteria that indicate which outpatient clients you will not see?

```{r}
q4 <-
  df %>%
  select(site_abbr, survey_04___1:survey_04_other) %>%
  filter_all(any_vars(. != 0))

q4_uniq_sites <-
  q4 %>%
  select(site_abbr) %>%
  unique() %>%
  nrow()
```

```{r}
q4_results <-
  q4 %>%
  select(-c(survey_04_exclude_young, survey_04_exclude_old, survey_04_other)) %>%
  pivot_longer(survey_04___1:survey_04___4, names_to = "exclusion_criteria", values_to = "count") %>%
  filter(count == 1) %>%
  unique() %>%
  mutate(exclusion_criteria = recode(exclusion_criteria,
    "survey_04___1" = "Catchment area",
    "survey_04___2" = "Exclusion of young children",
    "survey_04___3" = "Exclusion of older youth/emerging adults",
    "survey_04___4" = "Other exclusion") %>%
      as_factor() %>%
      fct_relevel(c("Catchment area", "Exclusion of young children", "Exclusion of older youth/emerging adults", "Other exclusion")))

catchment_sites <-
  q4_results %>%
  filter(exclusion_criteria == "Catchment area") %>%
  select(site_abbr) %>%
  unlist %>%
  paste(., collapse=", ")

young_age_sites <-
  q4_results %>%
  filter(exclusion_criteria == "Exclusion of young children") %>%
  select(site_abbr) %>%
  unlist %>%
  paste(., collapse=", ")

old_age_sites <-
  q4_results %>%
  filter(exclusion_criteria == "Exclusion of older youth/emerging adults") %>%
  select(site_abbr) %>%
  unlist %>%
  paste(., collapse=", ")

other_exclude_sites <-
  q4_results %>%
  filter(exclusion_criteria == "Other exclusion") %>%
  select(site_abbr) %>%
  unlist %>%
  paste(., collapse=", ")
```

```{r}
q4_results %>%
  group_by(exclusion_criteria) %>%
  summarize(count = n()) %>%
  mutate(count_scaled = count/q4_uniq_sites * 100) %>%
  ungroup() %>%
  mutate(site = case_when(exclusion_criteria == "Catchment area" ~ catchment_sites,
                          exclusion_criteria == "Exclusion of young children" ~ young_age_sites,
                          exclusion_criteria == "Exclusion of older youth/emerging adults" ~ old_age_sites,
                          exclusion_criteria == "Other exclusion" ~ other_exclude_sites)) %>%  
  gt() %>%
  gt_plt_bar_pct(column = count_scaled, scaled = TRUE) %>%
  cols_label(
    exclusion_criteria = "Exclusion criteria",
    count = "# of responses",
    count_scaled = ""
  ) %>%
  cols_align(align = c("left"),
             columns = exclusion_criteria) %>%
  cols_width(3 ~ px(125)) %>%
  gt_theme_538()
```

<br>

```{r}
exclude_age <-
  df %>%
  select(site_abbr, survey_04_exclude_young, survey_04_exclude_old) %>%
  mutate(exclude_age = case_when(!is.na(survey_04_exclude_young) & !is.na(survey_04_exclude_old) ~ glue("> {survey_04_exclude_young} and < {survey_04_exclude_old}"),
                                 !is.na(survey_04_exclude_young) ~ glue("> {survey_04_exclude_young}"),
                                 !is.na(survey_04_exclude_old) ~ glue("< {survey_04_exclude_old}"))) %>%
  select(site_abbr, exclude_age) %>%
  filter(!is.na(exclude_age))

exclude_age %>%
  gt() %>%
  cols_label(
    site_abbr = "Site",
    exclude_age = md("Age ranges **included**")
  ) %>%
  gt_theme_538()
```

<br>

```{r}
exclude_other <-
  df %>%
  select(site_abbr, survey_04_other) %>%
  filter(!is.na(survey_04_other))

exclude_other %>%
  gt()  %>%
  cols_label(
    site_abbr = "Site",
    survey_04_other = "Other exclusion criteria"
  ) %>%
  gt_theme_538()
```

### 5. Is first outpatient clinical assessment assigned on a first come, first served basis?

```{r}
q5 <-
  df %>%
  select(site_abbr, survey_05, survey_05_other) %>%
  filter(!is.na(survey_05))

q5_uniq_sites <- q5 %>%
  select(site_abbr) %>%
  unique() %>%
  nrow()
```

```{r}
q5_results <-
  q5 %>%
  unique() %>%
  mutate(survey_05 = recode(survey_05,
                            "1" = "Yes",
                            "0" = "No",
                            "2" = "Other") %>%
           as_factor() %>%
           fct_relevel(c("Yes", "No", "Other")))

outpatient_yes_sites <-
  q5_results %>%
  filter(survey_05 == "Yes") %>%
  select(site_abbr) %>%
  unlist %>%
  paste(., collapse=", ")

outpatient_no_sites <-
  q5_results %>%
  filter(survey_05 == "No") %>%
  select(site_abbr) %>%
  unlist %>%
  paste(., collapse=", ")

outpatient_other_sites <-
  q5_results %>%
  filter(survey_05 == "Other") %>%
  select(site_abbr) %>%
  unlist %>%
  paste(., collapse=", ")

q5_results %>%
  group_by(survey_05) %>%
  summarize(count = n()) %>%
  mutate(count_scaled = count/q5_uniq_sites * 100) %>%
  ungroup() %>%
  mutate(site = case_when(survey_05 == "Yes" ~ outpatient_yes_sites,
                          survey_05 == "No" ~ outpatient_no_sites,
                          survey_05 == "Other" ~ outpatient_other_sites)) %>%
  gt() %>%
  gt_plt_bar_pct(column = count_scaled, scaled = TRUE) %>%
  cols_label(
    survey_05 = "Response",
    count = "# of responses",
    count_scaled = "",
    site = "Sites"
  )  %>%
  cols_align(align = c("left"),
             columns = survey_05) %>%
  cols_width(3 ~ px(125)) %>%
  gt_theme_538()
```

<br>

```{r}
q5 %>%
  filter(!is.na(survey_05_other)) %>%
  select(-survey_05) %>%
  gt() %>%
  cols_label(
    site_abbr = "Site",
    survey_05_other = "Other response"
  ) %>%
  gt_theme_538()
```

### 6. Across your child & youth outpatient mental health service, what is the current average wait time from first referral to initial outpatient clinical assessment?

```{r}
q6 <-
  df %>%
  select(site_abbr, survey_06, survey_06_other) %>%
  filter(!is.na(survey_06))

q6_uniq_sites <-
  q6 %>%
  select(site_abbr) %>%
  unique() %>%
  nrow()
```

```{r}
q6_results <-
  q6 %>%
  unique() %>%
  mutate(survey_06 = recode(survey_06,
                            "1" = "< 1 month",
                            "2" = "1-2 months",
                            "3" = "3-6 months",
                            "4" = "7-9 months",
                            "5" = "10-12 months",
                            "6" = "12+ months") %>%
           as_factor() %>%
           fct_relevel(c("C< 1 month", "1-2 months", "3-6 months", "7-9 months", "10-12 months", "12+ months")))

wait_1_sites <-
  q6_results %>%
  filter(survey_06 == "< 1 month") %>%
  select(site_abbr) %>%
  unlist %>%
  paste(., collapse=", ")

wait_2_sites <-
  q6_results %>%
  filter(survey_06 == "1-2 months") %>%
  select(site_abbr) %>%
  unlist %>%
  paste(., collapse=", ")

wait_3_sites <-
  q6_results %>%
  filter(survey_06 == "3-6 months") %>%
  select(site_abbr) %>%
  unlist %>%
  paste(., collapse=", ")

wait_4_sites <-
  q6_results %>%
  filter(survey_06 == "7-9 months") %>%
  select(site_abbr) %>%
  unlist %>%
  paste(., collapse=", ")

wait_5_sites <-
  q6_results %>%
  filter(survey_06 == "10-12 months") %>%
  select(site_abbr) %>%
  unlist %>%
  paste(., collapse=", ")

wait_6_sites <-
  q6_results %>%
  filter(survey_06 == "12+ months") %>%
  select(site_abbr) %>%
  unlist %>%
  paste(., collapse=", ")

q6_results %>%
  group_by(survey_06) %>%
  summarize(count = n()) %>%
  mutate(count_scaled = count/q6_uniq_sites * 100) %>%
  ungroup() %>%
  mutate(site = case_when(survey_06 == "< 1 month" ~ wait_1_sites,
                          survey_06 == "1-2 months" ~ wait_2_sites,
                          survey_06 == "3-6 months" ~ wait_3_sites,
                          survey_06 == "7-9 months" ~ wait_4_sites,
                          survey_06 == "10-12 months" ~ wait_5_sites,
                          survey_06 == "12+ months" ~ wait_6_sites)) %>%
  gt() %>%
  gt_plt_bar_pct(column = count_scaled, scaled = TRUE) %>%
  cols_label(
    survey_06 = "Average wait time",
    count = "# of responses",
    count_scaled = "",
    site = "Sites"
  ) %>%
  cols_align(align = c("left"),
             columns = survey_06) %>%
  cols_width(3 ~ px(125)) %>%
  gt_theme_538()
```

### 7. Initial outpatient clinical assessments completed by:

```{r}
q7 <-
  df %>%
  select(site_abbr, survey_07) %>%
  filter(!is.na(survey_07))

q7_uniq_sites <-
  q7 %>%
  select(site_abbr) %>%
  unique() %>%
  nrow()
```

```{r}
q7_results <-
  q7 %>%
  unique() %>%
  mutate(survey_07 = recode(survey_07,
                            "1" = "MD only",
                            "2" = "Psychologist only",
                            "3" = "Other allied health staff only",
                            "4" = "MD, psychologist or other allied health clinician",
                            "5" = "Always multidisciplinary") %>%
           as_factor())

md_sites <-
  q7_results %>%
  filter(survey_07 == "MD only") %>%
  select(site_abbr) %>%
  unlist %>%
  paste(., collapse=", ")

psych_sites <-
  q7_results %>%
  filter(survey_07 == "Psychologist only") %>%
  select(site_abbr) %>%
  unlist %>%
  paste(., collapse=", ")

other_allied_sites <-
  q7_results %>%
  filter(survey_07 == "Other allied health staff only") %>%
  select(site_abbr) %>%
  unlist %>%
  paste(., collapse=", ")

either_md_allied_sites <-
  q7_results %>%
  filter(survey_07 == "MD, psychologist or other allied health clinician") %>%
  select(site_abbr) %>%
  unlist %>%
  paste(., collapse=", ")

multi_sites <-
  q7_results %>%
  filter(survey_07 == "Always multidisciplinary") %>%
  select(site_abbr) %>%
  unlist %>%
  paste(., collapse=", ")

q7_results %>%
  group_by(survey_07) %>%
  summarize(count = n()) %>%
  mutate(count_scaled = count/q7_uniq_sites * 100) %>%
  ungroup() %>%
  mutate(site = case_when(survey_07 == "MD only" ~ md_sites,
                          survey_07 == "MD, psychologist or other allied health clinician" ~ either_md_allied_sites,
                          survey_07 == "Always multidisciplinary" ~ multi_sites)) %>%
  gt() %>%
  gt_plt_bar_pct(column = count_scaled, scaled = TRUE) %>%
  cols_label(
    survey_07 = "Completed by",
    count = "# of responses",
    count_scaled = "",
    site = "Sites"
  ) %>%
  cols_align(align = c("left"),
             columns = survey_07) %>%
  cols_width(3 ~ px(125)) %>%
  gt_theme_538()
```

### 8. How many FTE MDs are there at your site/centre providing outpatient mental health assessment/care for children and youth?

```{r}
df %>%
  select(site_abbr, survey_08) %>%
  arrange(site_abbr) %>%
  gt() %>%
  cols_label(
    site_abbr = "Site",
    survey_08 = "MD"
  ) %>%
  gt_theme_538()
```

### 9. How many FTE allied health are there?

NOTE: No FTE allied health from Unity Health and Women's College.

```{r}
q9 <-
  df %>%
  select(site_abbr, survey_09_psych:survey_09_other3) %>%
  select(!contains("_equal")) %>%
  mutate_all(~na_if(., 0)) %>%
  mutate(survey_09_other1_title = case_when(
    survey_09_other1_title %in% c("occupational therapist", "Occupational Therapists") ~ "Occupational therapist",
    survey_09_other1_title == "intake specialist" ~ "Intake specialist",
    survey_09_other1_title == "ECE" ~ "ECE",
    survey_09_other1_title == "Mental health nurse" ~ "Mental health nurse",
    survey_09_other1_title == "psychometrist" ~"Psychometrist"
  )) %>%
  unite("other", survey_09_other1_title:survey_09_other1, sep = " - ", na.rm = TRUE, remove = TRUE) %>%
  unique()

q9 <- q9[, colSums(sapply(q9, is.na)) != nrow(q9)]

no_allied_sites <- q9[rowSums(is.na(q9)) == ncol(q9) - 1, ]$site_abbr

q9 <- q9[rowSums(is.na(q9)) != ncol(q9) - 1, ]
```

```{r}
q9 %>%
  arrange(site_abbr) %>%
  gt() %>%
  fmt_missing(columns = everything(), missing_text = "—") %>%
  cols_label(
    site_abbr = "Site",
    survey_09_psych = "Psychologist",
    survey_09_psych_assoc = "Psych associate",
    survey_09_soc = "Social worker",
    survey_09_rn = "Registered nurse",
    survey_09_np = "Nurse practitioner",
    survey_09_cyw = "CYW",
    survey_09_bcba = "BCBA",
    other = "Other"
  ) %>%
  gt_theme_538()
```

### 10. Does your site/centre track what proportion of outpatient clients are offered ongoing outpatient care/treatment services following an initial child & youth mental health assessment?

```{r}
q10 <-
  df %>%
  select(site_abbr, survey_10:survey_10_other) %>%
  filter_all(any_vars(. != 0))

q10_uniq_sites <-
  q10 %>%
  select(site_abbr) %>%
  unique() %>%
  nrow()
```

```{r}
q10_results <-
  q10 %>%
  select(-c(survey_10_percent, survey_10_other)) %>%
  unique() %>%
  mutate(survey_10 = recode(survey_10,
                            "1" = "Tracked",
                            "2" = "Tracked for some but not all services",
                            "3" = "Not tracked",
                            "4" = "Don't know") %>%
           as_factor())

tracked_sites <-
  q10_results %>%
  filter(survey_10 == "Tracked") %>%
  select(site_abbr) %>%
  unlist %>%
  paste(., collapse=", ")

some_tracked_sites <-
  q10_results %>%
  filter(survey_10 == "Tracked for some but not all services") %>%
  select(site_abbr) %>%
  unlist %>%
  paste(., collapse=", ")

untracked_sites <-
  q10_results %>%
  filter(survey_10 == "Not tracked") %>%
  select(site_abbr) %>%
  unlist %>%
  paste(., collapse=", ")

tracking_unk_sites <-
  q10_results %>%
  filter(survey_10 == "Don't know") %>%
  select(site_abbr) %>%
  unlist %>%
  paste(., collapse=", ")

q10_results %>%
  group_by(survey_10) %>%
  summarize(count = n()) %>%
  mutate(count_scaled = count/q10_uniq_sites * 100) %>%
  ungroup() %>%
  mutate(site = case_when(survey_10 == "Tracked" ~ tracked_sites,
                          survey_10 == "Tracked for some but not all services" ~ some_tracked_sites,
                          survey_10 == "Not tracked" ~ untracked_sites,
                          survey_10 == "Don't know" ~ tracking_unk_sites)) %>%
  gt() %>%
  gt_plt_bar_pct(column = count_scaled, scaled = TRUE) %>%
  cols_label(
    survey_10 = "Response",
    count = "# of responses",
    count_scaled = "",
    site = "Sites"
  ) %>%
  cols_width(3 ~ px(125)) %>%
  cols_align(align = c("left"),
             columns = survey_10) %>%
  gt_theme_538()  
```

<br>

```{r}
df %>%
  select(site_abbr, survey_10, survey_10_percent, survey_10_other) %>%
  filter(survey_10 %in% c(1, 2)) %>%
  mutate(survey_10_recode = recode(survey_10,
                            "1" = "Tracked",
                            "2" = "Tracked for some but not all services",
                            "3" = "Not tracked",
                            "4" = "Don't know"),
         scale_bar = survey_10_percent) %>%
  select(site_abbr, survey_10_recode, survey_10_percent, scale_bar, survey_10_other) %>%
  unique() %>%
  arrange(site_abbr) %>%
  gt() %>%
  gt_plt_bar_pct(column = scale_bar, scaled = TRUE) %>%
  cols_label(
    site_abbr = "Site",
    survey_10_recode = "Tracking status",
    survey_10_percent = "%",
    scale_bar = "",
    survey_10_other = "Other"
  ) %>%
  cols_width(4 ~ px(125)) %>%
  gt_theme_538()
```

### 11. Does your site/centre use specific criteria to determine which outpatient clients are provided with any ongoing mental health care after an initial assessment is completed?


```{r}
q11 <-
  df %>%
  select(site_abbr, survey_11:survey_11_some) %>%
  filter_all(any_vars(. != 0))

q11_uniq_sites <-
  q11 %>%
  select(site_abbr) %>%
  unique() %>%
  nrow()
```

```{r}
q11_results <-
  q11 %>%
  unique() %>%
  mutate(survey_11_recode = recode(survey_11,
                                   "1" = "All programs/services have specific criteria",
                                   "2" = "Some programs/services have specific criteria",
                                   "3" = "None") %>%
           as_factor() %>%
           fct_relevel(c("All programs/services have specific criteria", "Some programs/services have specific criteria", "None")),
         survey_11_explain = case_when(!is.na(survey_11_all) ~ survey_11_all,
                                       !is.na(survey_11_some) ~ survey_11_some))

crit_all_sites <-
  q11_results %>%
  filter(survey_11 == 1) %>%
  select(site_abbr) %>%
  unlist %>%
  paste(., collapse=", ")

crit_some_sites <-
  q11_results %>%
  filter(survey_11 == 2) %>%
  select(site_abbr) %>%
  unlist %>%
  paste(., collapse=", ")

crit_none_sites <-
  q11_results %>%
  filter(survey_11 == 3) %>%
  select(site_abbr) %>%
  unlist %>%
  paste(., collapse=", ")
```

```{r}
q11_results %>%
  group_by(survey_11_recode) %>%
  summarize(count = n()) %>%
  mutate(count_scaled = count/q11_uniq_sites * 100) %>%
  ungroup() %>%
  mutate(site = case_when(survey_11_recode == "All programs/services have specific criteria" ~ crit_all_sites,
                          survey_11_recode == "Some programs/services have specific criteria" ~ crit_some_sites,
                          survey_11_recode == "None" ~ crit_none_sites)) %>%
  gt() %>%
  gt_plt_bar_pct(column = count_scaled, scaled = TRUE) %>%
  cols_label(
    survey_11_recode = "Response",
    count = "# of responses",
    count_scaled = ""
  ) %>%
  cols_width(3 ~ px(125)) %>%
  cols_align(align = c("left"),
             columns = survey_11_recode) %>%
  gt_theme_538()    
```

<br>

```{r}
q11_results %>%
  filter(survey_11 %in% c(1, 2)) %>%
  select(site_abbr, survey_11_recode, survey_11_explain) %>%
  arrange(survey_11_recode) %>%
  gt() %>%
  cols_label(
    site_abbr = "Site",
    survey_11_recode = "Criteria",
    survey_11_explain = "Please specify"
  ) %>%
  cols_align(align = c("left")) %>%
  gt_theme_538()
```

### 12. Which of the following outpatient mental health treatment services are offered at your centre?

```{r}
q12 <-
  df %>%
  select(site_abbr, survey_12_group___1:survey_12_day_tx_wait) %>%
  filter_all(any_vars(. != 0))

q12_uniq_sites <-
  q12 %>%
  select(site_abbr) %>%
  unique() %>%
  nrow()
```

```{r}
q12_results <-
  q12 %>%
  select(site_abbr, survey_12_group___1:survey_12_group___5, survey_12_individual___1:survey_12_individual___5, survey_12_cont___1:survey_12_cont___9) %>%   
  pivot_longer(survey_12_group___1:survey_12_cont___9, names_to = "psychotherapy", values_to = "count") %>%
  filter(count == 1) %>%
  unique() %>%
  mutate(setting = case_when(str_detect(psychotherapy, "group") ~ "Group",
                             str_detect(psychotherapy, "individual") ~ "Individual",
                             str_detect(psychotherapy, "cont") ~ "Other"),
         psychotherapy_recode = case_when(str_detect(psychotherapy, "[individual|group]___1") ~ "CBT",
                                          str_detect(psychotherapy, "[individual|group]___2") ~ "DBT",
                                          str_detect(psychotherapy, "[individual|group]___3") ~ "IPT",
                                          str_detect(psychotherapy, "[individual|group]___4") ~ "Other",
                                          str_detect(psychotherapy, "[individual|group]___5") ~ "None",
                                          str_detect(psychotherapy, "cont___1") ~ "Family therapy",
                                          str_detect(psychotherapy, "cont___2") ~ "Unstructured supportive group therapy",
                                          str_detect(psychotherapy, "cont___3") ~ "Unstructured supportive individual therapy",
                                          str_detect(psychotherapy, "cont___4") ~ "Medication support by MD/nurse practitioner",
                                          str_detect(psychotherapy, "cont___5") ~ "System/Transition navigators",
                                          str_detect(psychotherapy, "cont___6") ~ "Urgent care clinic",
                                          str_detect(psychotherapy, "cont___7") ~ "Urgent assessment",
                                          str_detect(psychotherapy, "cont___8") ~ "Day treatment",
                                          str_detect(psychotherapy, "cont___9") ~ "Other") %>%
           as_factor() %>%
           fct_relevel(c("CBT", "DBT", "IPT", "Family therapy", "Unstructured supportive group therapy", "Unstructured supportive individual therapy", "Medication support by MD/nurse practitioner", "System/Transition navigators", "Urgent care clinic", "Urgent assessment", "Day treatment", "Other", "None")))

cbt_g_sites <-
  q12_results %>%
  filter(setting == "Group" & psychotherapy_recode == "CBT") %>%
  select(site_abbr) %>%
  unlist %>%
  paste(., collapse=", ")

dbt_g_sites <-
  q12_results %>%
  filter(setting == "Group" & psychotherapy_recode == "DBT") %>%
  select(site_abbr) %>%
  unlist %>%
  paste(., collapse=", ")

ipt_g_sites <-
  q12_results %>%
  filter(setting == "Group" & psychotherapy_recode == "IPT") %>%
  select(site_abbr) %>%
  unlist %>%
  paste(., collapse=", ")

other_g_sites <-
  q12_results %>%
  filter(setting == "Group" & psychotherapy_recode == "Other") %>%
  select(site_abbr) %>%
  unlist %>%
  paste(., collapse=", ")

none_g_sites <-
  q12_results %>%
  filter(setting == "Group" & psychotherapy_recode == "None") %>%
  select(site_abbr) %>%
  unlist %>%
  paste(., collapse=", ")

cbt_i_sites <-
  q12_results %>%
  filter(setting == "Individual" & psychotherapy_recode == "CBT") %>%
  select(site_abbr) %>%
  unlist %>%
  paste(., collapse=", ")

dbt_i_sites <-
  q12_results %>%
  filter(setting == "Individual" & psychotherapy_recode == "DBT") %>%
  select(site_abbr) %>%
  unlist %>%
  paste(., collapse=", ")

ipt_i_sites <-
  q12_results %>%
  filter(setting == "Individual" & psychotherapy_recode == "IPT") %>%
  select(site_abbr) %>%
  unlist %>%
  paste(., collapse=", ")

other_i_sites <-
  q12_results %>%
  filter(setting == "Individual" & psychotherapy_recode == "Other") %>%
  select(site_abbr) %>%
  unlist %>%
  paste(., collapse=", ")

none_i_sites <-
  q12_results %>%
  filter(setting == "Individual" & psychotherapy_recode == "None") %>%
  select(site_abbr) %>%
  unlist %>%
  paste(., collapse=", ")

ft_sites <-
  q12_results %>%
  filter(setting == "Other" & psychotherapy_recode == "Family therapy") %>%
  select(site_abbr) %>%
  unlist %>%
  paste(., collapse=", ")

usgt_sites <-
  q12_results %>%
  filter(setting == "Other" & psychotherapy_recode == "Unstructured supportive group therapy") %>%
  select(site_abbr) %>%
  unlist %>%
  paste(., collapse=", ")

usit_sites <-
  q12_results %>%
  filter(setting == "Other" & psychotherapy_recode == "Unstructured supportive individual therapy") %>%
  select(site_abbr) %>%
  unlist %>%
  paste(., collapse=", ")

md_support_sites <-
  q12_results %>%
  filter(setting == "Other" & psychotherapy_recode == "Medication support by MD/nurse practitioner") %>%
  select(site_abbr) %>%
  unlist %>%
  paste(., collapse=", ")

sys_nav_sites <-
  q12_results %>%
  filter(setting == "Other" & psychotherapy_recode == "System/Transition navigators") %>%
  select(site_abbr) %>%
  unlist %>%
  paste(., collapse=", ")

ucc_sites <-
  q12_results %>%
  filter(setting == "Other" & psychotherapy_recode == "Urgent care clinic") %>%
  select(site_abbr) %>%
  unlist %>%
  paste(., collapse=", ")

ua_sites <-
  q12_results %>%
  filter(setting == "Other" & psychotherapy_recode == "Family therapy") %>%
  select(site_abbr) %>%
  unlist %>%
  paste(., collapse=", ")

dt_sites <-
  q12_results %>%
  filter(setting == "Other" & psychotherapy_recode == "Day treatment") %>%
  select(site_abbr) %>%
  unlist %>%
  paste(., collapse=", ")

other_other_sites <-
  q12_results %>%
  filter(setting == "Other" & psychotherapy_recode == "Other") %>%
  select(site_abbr) %>%
  unlist %>%
  paste(., collapse=", ")
```

```{r}
q12_results %>%
  group_by(setting, psychotherapy_recode) %>%
  summarize(count = n()) %>%
  mutate(count_scaled = count/q12_uniq_sites * 100) %>%
  ungroup() %>%
  mutate(site = case_when(setting == "Group" & psychotherapy_recode == "CBT" ~ cbt_g_sites,
                          setting == "Group" & psychotherapy_recode == "DBT" ~ dbt_g_sites,
                          setting == "Group" & psychotherapy_recode == "IPT" ~ ipt_g_sites,
                          setting == "Group" & psychotherapy_recode == "Other" ~ other_g_sites,
                          setting == "Group" & psychotherapy_recode == "None" ~ none_g_sites,
                          setting == "Individual" & psychotherapy_recode == "CBT" ~ cbt_i_sites,
                          setting == "Individual" & psychotherapy_recode == "DBT" ~ dbt_i_sites,
                          setting == "Individual" & psychotherapy_recode == "IPT" ~ ipt_i_sites,
                          setting == "Individual" & psychotherapy_recode == "Other" ~ other_i_sites,
                          setting == "Individual" & psychotherapy_recode == "None" ~ none_i_sites,
                          setting == "Other" & psychotherapy_recode == "Family therapy" ~ ft_sites,
                          setting == "Other" & psychotherapy_recode == "Unstructured supportive group therapy" ~ usgt_sites,
                          setting == "Other" & psychotherapy_recode == "Unstructured supportive individual therapy" ~ usit_sites,
                          setting == "Other" & psychotherapy_recode == "Medication support by MD/nurse practitioner" ~ md_support_sites,
                          setting == "Other" & psychotherapy_recode == "System/Transition navigators" ~ sys_nav_sites,
                          setting == "Other" & psychotherapy_recode == "Urgent care clinic" ~ ucc_sites,
                          setting == "Other" & psychotherapy_recode == "Urgent assessment" ~ ua_sites,
                          setting == "Other" & psychotherapy_recode == "Day treatment" ~ dt_sites,
                          setting == "Other" & psychotherapy_recode == "Other" ~ other_other_sites
  )) %>%
  group_by(setting) %>%
  gt() %>%
  gt_plt_bar_pct(column = count_scaled, scaled = TRUE) %>%
  cols_label(
    setting = "Setting",
    psychotherapy_recode = "Treatment",
    count = "# of responses",
    count_scaled = "",
    site = "Sites"
  ) %>%
  cols_align(align = c("left"),
             columns = psychotherapy_recode) %>%
  cols_width(4 ~ px(125)) %>%
  gt_theme_538()
```

<br>

```{r}
q12 %>%
  select(site_abbr, survey_12_group_other, survey_12_individual_other, survey_12_cont_other) %>%
  pivot_longer(survey_12_group_other:survey_12_cont_other, names_to = "setting", values_to = "other") %>%
  filter(!is.na(other)) %>%
  mutate(setting = case_when(str_detect(setting, "group") ~ "Group",
                             str_detect(setting, "individual") ~ "Individual",
                             str_detect(setting, "cont") ~ "Other") %>%
           as_factor() %>%
           fct_relevel(c("Group", "Individual", "Other"))) %>%
  arrange(setting) %>%
  group_by(setting) %>%
  gt() %>%
  cols_label(
    site_abbr = "Site",
    other = "Other treatment service"
  ) %>%
  gt_theme_538()
```

<br>

```{r}
q12 %>%
  select(site_abbr, contains("wait")) %>%
  pivot_longer(survey_12_cbt_group_wait:survey_12_day_tx_wait, names_to = "treatment", values_to = "wait") %>%
  filter(!is.na(wait)) %>%
  group_by(treatment) %>%
  arrange(treatment)
```

### 12b. Is the group/individual (CBT, DBT, IPT) psychotherapy approach used standardized across your service?

```{r}
q12_psych <-
  q12 %>%
  select(site_abbr, survey_12_part) %>%
  filter(!is.na(survey_12_part)) %>%
  unique() %>%
  mutate(survey_12_part_recode = recode(survey_12_part,
                                        "1" = "Yes",
                                        "0" = "No",
                                        "2" = "Don't know") %>%
           as_factor() %>%
           fct_relevel(c("Yes", "No", "Don't know")))

standard_yes_sites <-
  q12_psych %>%
  filter(survey_12_part == 1) %>%
  select(site_abbr) %>%
  unlist %>%
  paste(., collapse=", ")

standard_no_sites <-
  q12_psych %>%
  filter(survey_12_part == 0) %>%
  select(site_abbr) %>%
  unlist %>%
  paste(., collapse=", ")

standard_unk_sites <-
  q12_psych %>%
  filter(survey_12_part == 2) %>%
  select(site_abbr) %>%
  unlist %>%
  paste(., collapse=", ")

q12_psych %>%
  group_by(survey_12_part_recode) %>%
  summarize(count = n()) %>%
  mutate(count_scaled = count/q12_uniq_sites * 100) %>%
  ungroup() %>%
  mutate(site = case_when(survey_12_part_recode == "Yes" ~ standard_yes_sites,
                          survey_12_part_recode == "No" ~ standard_no_sites,
                          survey_12_part_recode == "Don't know" ~ standard_unk_sites)) %>%
  gt() %>%
  gt_plt_bar_pct(column = count_scaled, scaled = TRUE) %>%
  cols_label(
    survey_12_part_recode = "Response",
    count = "# of responses",
    count_scaled = "",
    site = "Sites"
  ) %>% 
  cols_width(3 ~ px(125)) %>%
  cols_align(align = c("left"),
             columns = survey_12_part_recode) %>%
  gt_theme_538()
```

### 12c. Please specify DBT model used:

```{r}
q12 %>%
  select(site_abbr, survey_12_dbt) %>%
  filter(!is.na(survey_12_dbt)) %>%
  gt() %>%
  cols_label(
    site_abbr = "Site",
    survey_12_dbt = "DBT Model"
  ) %>%
  gt_theme_538()
```

### 13. Does your site have pre-defined criteria to indicate when outpatient clients that are currently receiving outpatient psychiatric/mental health care in your service are discharged/transitioned out of your service and over to their GP, primary care, community, or other services for ongoing mental health care?

```{r}
q13 <-
  df %>%
  select(site_abbr, survey_13, survey_13_specify)

q13_uniq_sites <-
  q13 %>%
  select(site_abbr) %>%
  unique() %>%
  nrow()
```

```{r}
q13_results <-
  q13 %>%
  unique() %>%
  mutate(survey_13_recode = recode(survey_13,
                                   "1" = "Yes",
                                   "0" = "No",
                                   "2" = "Don't know") %>%
           as_factor() %>%
           fct_relevel(c("Yes", "No", "Don't know")))

discharge_yes_sites <-
  q13_results %>%
  filter(survey_13 == 1) %>%
  select(site_abbr) %>%
  unlist %>%
  paste(., collapse=", ")

discharge_no_sites <-
  q13_results %>%
  filter(survey_13 == 0) %>%
  select(site_abbr) %>%
  unlist %>%
  paste(., collapse=", ")

discharge_unk_sites <-
  q13_results %>%
  filter(survey_13 == 2) %>%
  select(site_abbr) %>%
  unlist %>%
  paste(., collapse=", ")
```

```{r}
q13_results %>%
  group_by(survey_13_recode) %>%
  summarize(count = n()) %>%
  mutate(count_scaled = count/q13_uniq_sites * 100) %>%
  ungroup() %>%
  mutate(site = case_when(survey_13_recode == "Yes" ~ discharge_yes_sites,
                          survey_13_recode == "No" ~ discharge_no_sites,
                          survey_13_recode == "Don't know" ~ discharge_unk_sites)) %>%
  gt() %>%
  gt_plt_bar_pct(column = count_scaled, scaled = TRUE) %>%
  cols_label(
    survey_13_recode = "Response",
    count = "# of responses",
    count_scaled = "",
    site = "Sites"
  ) %>% 
  cols_width(3 ~ px(125)) %>%
  cols_align(align = c("left"),
             columns = survey_13_recode) %>%
  gt_theme_538()
```

<br>

Sites which specified their pre-defined criteria are summarized below:
```{r}
q13 %>%
  select(site_abbr, survey_13_specify) %>%
  filter(!is.na(survey_13_specify)) %>%
  gt() %>%
  cols_label(
    site_abbr = "Site",
    survey_13_specify = "Specify"
  ) %>%
  gt_theme_538()
```

## Logistics

```{r}
survey_logistics <-
  df %>%
  select(site_abbr, survey_14:survey_21)

survey_logistics <-
  survey_logistics[rowSums(is.na(survey_logistics)) != ncol(survey_logistics) - 1, ]
```

For the survey logistics section, we received responses from **`r survey_logistics %>% nrow()`** of the **`r df %>% nrow()`** site managers.

<br>

### 14. Survey questions were clearly worded and easy to respond to:

```{r}
q14 <-
  survey_logistics %>%
  select(site_abbr, survey_14) %>%
  filter(!is.na(survey_14)) %>%
  mutate(survey_14_recode = recode(survey_14,
                                   "1" = "Yes",
                                   "2" = "No"))

q14_responses <- nrow(q14)

q14 %>%
  group_by(survey_14_recode) %>%
  summarize(count = n()) %>%
  arrange(count) %>%
  mutate(count_scaled = count/q14_responses * 100) %>%
  gt() %>%
  gt_plt_bar_pct(column = count_scaled, scaled = TRUE) %>%
  cols_label(
    survey_14_recode = "Response",
    count = "# of responses",
    count_scaled = ""
  ) %>%
  cols_width(3 ~ px(125)) %>%
  gt_theme_538()
```

### 15. This survey took me:

```{r}
q15 <-
  survey_logistics %>%
  select(site_abbr, survey_15) %>%
  filter(!is.na(survey_15)) %>%
  mutate(survey_15_recode = recode(survey_15,
                                   "1" = "5-10 min",
                                   "2" = "10-15 min",
                                   "3" = "15-20 min",
                                   "4" = ">20 min"))

q15_responses <- nrow(q15)

q15 %>%
  group_by(survey_15_recode) %>%
  summarize(count = n()) %>%
  arrange(count) %>%
  mutate(count_scaled = count/q15_responses * 100) %>%
  gt() %>%
  gt_plt_bar_pct(column = count_scaled, scaled = TRUE) %>%
  cols_label(
    survey_15_recode = "Response",
    count = "# of responses",
    count_scaled = ""
  ) %>%
  cols_width(3 ~ px(125)) %>%
  gt_theme_538()
```

### 16. The length of this survey was:

```{r}
q16 <-
  survey_logistics %>%
  select(site_abbr, survey_16) %>%
  filter(!is.na(survey_16)) %>%
  mutate(survey_16_recode = recode(survey_16,
                                   "1" = "Too long",
                                   "2" = "Perfect",
                                   "3" = "Would have been OK and manageable if the survey were a little longer"))

q16_responses <- nrow(q16)

q16 %>%
  group_by(survey_16_recode) %>%
  summarize(count = n()) %>%
  arrange(desc(count)) %>%
  mutate(count_scaled = count/q16_responses * 100) %>%
  gt() %>%
  gt_plt_bar_pct(column = count_scaled, scaled = TRUE) %>%
  cols_label(
    survey_16_recode = "Response",
    count = "# of responses",
    count_scaled = ""
  ) %>%
  cols_width(3 ~ px(125)) %>%
  gt_theme_538()
```

### 17. Do you think the information collected in this survey would be useful to enhance knowledge and connectivity across our Division?
  
```{r}
q17 <-
  survey_logistics %>%
  select(site_abbr, survey_17) %>%
  filter(!is.na(survey_17)) %>%
  mutate(survey_17_recode = recode(survey_17,
                                   "1" = "Yes",
                                   "0" = "No",
                                   "2" = "Don't know") %>%
           as_factor() %>%
           fct_relevel(c("Yes", "No", "Don't know")))

q17_responses <- nrow(q17)

q17 %>%
  group_by(survey_17_recode) %>%
  summarize(count = n()) %>%
  arrange(desc(count)) %>%
  mutate(count_scaled = count/q17_responses * 100) %>%
  gt() %>%
  gt_plt_bar_pct(column = count_scaled, scaled = TRUE) %>%
  cols_label(
    survey_17_recode = "Response",
    count = "# of responses",
    count_scaled = ""
  ) %>%
  cols_width(3 ~ px(125)) %>%
  gt_theme_538()
```

### 18. Would you be willing to be contacted to contribute to a meeting to discuss what information about outpatient care delivery across the Division and GTA would be helpful to your site and how the information collected could be shared/presented to make it most useful? What format for this meeting would you prefer?

```{r}
q18 <-
  survey_logistics %>%
  select(site_abbr, survey_18, survey_18_format, survey_18_format_b) %>%
  filter(!is.na(survey_18)) %>%
  mutate(contact = recode(survey_18,
                          "1" = "Yes",
                          "0" = "No",
                          "2" = "Maybe") %>%
           as_factor(),
         meeting_format = recode(survey_18_format,
                                 "1" = "Individual",
                                 "2" = "Group of different stakeholders",
                                 "3" = "Group of managers only") %>%
           as_factor(),
         meeting_where = recode(survey_18_format_b,
                                "1" = "In person",
                                "2" = "Virtual") %>%
           as_factor()) %>%
  select(site_abbr, contact, meeting_format, meeting_where)
```

<br>

```{r}
q18 %>%
  select(-site_abbr) %>%
  tbl_summary(
    label = list(contact ~ "Willing to be contacted?",
                 meeting_format ~ "Meeting format",
                 meeting_where ~ "Meeting location")
  ) %>%
  modify_header(label = "")
```

### 19. Do you have any recommendations on which topics to cover or questions you would like to see in future surveys?

```{r}
q19 <-
  survey_logistics %>%
  select(site_abbr, survey_19) %>%
  filter(!is.na(survey_19))

q19 %>%
  arrange(site_abbr) %>%
  gt() %>%
  cols_label(
    site_abbr = "Site",
    survey_19 = "Recommendations") %>%
  gt_theme_538()
```

### 20. Do you have any recommendations for how we can improve our survey approach?

No response.

```{r, include=FALSE}
q20 <-
  survey_logistics %>%
  select(site_abbr, survey_20) %>%
  filter(!is.na(survey_20))

q20
```

### 21. Open text option for any additional feedback:
  
No response.
  
```{r, include=FALSE}
q21 <-
  survey_logistics %>%
  select(site_abbr, survey_21) %>%
  filter(!is.na(survey_21))

q21
```
